$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-01 paper/paper.tex
Update paper.tex

The complete structural congruence is given in \autoref{app:struct}.
\autoref{fig:struct-cong-base} lists the base cases.

@@

@@

\subsection{Operational Semantics}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{operational-semantics}

The operational semantics of the \picalc{} is defined via a reduction relation in \autoref{fig:reduction}.
In rule $\constr{comm}$, processes in parallel reduce when they communicate over the same index ${i}$.
The input process $\recv{i}P$ substitutes in $P$ references to the most immediate variable placeholder with references to the variable sent by the output process $\send{i}{j}{Q}$.
The continuation $\subst{P}{j}{0}$ is then \emph{lowered} --- all variable references are decreased by one.
Reduction is closed under parallel composition (rule $\constr{par}$), scope restriction (rule $\constr{res}$) and structural congruence (rule $\constr{struct}$) 
--- notably, not under input nor output, otherwise the sequencing of actions would not be preserved \cite{Sangio01}.
%In  \autoref{subject-reduction} we prove that if $P$ reduces to $Q$ and $P$ is well-typed, so is $Q$.

\todo{this paragraph below is not clear}
Notice that the reduction relation in \autoref{fig:reduction} is effectful: it consumes the channel over which communication occurs.
If the channel is external to $P$ (it resides in its context) then the context in which $Q$ is typed must change.
To keep track of this information, we lift the index of the channel to the type level.
We use a $dec$ function to decrement the index of the channel every time we come out of a binder.
This function saturates at $\constr{internal}$ --- meaning communication happens internally to the process.

>>>>

Structural congruence $\eqeq$ is fully defined in \autoref{app:struct}.
\autoref{fig:struct-cong-base} lists the base cases.

@@

The first three rules on $\constr{comp}$ state respectively, associativity, symmetry, and $\PO$ as the neutral element for parallel composition.
The last three rules on $\constr{scope}$ state respectively, garbage collection, scope extrusion and commutativity of restrictions.

@@

\subsection{Reduction Relation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{operational-semantics}

The operational semantics of the \picalc{} is defined via a reduction relation $\reduce{}$ in \autoref{fig:reduction}.
In rule $\constr{comm}$, processes in parallel reduce when they communicate over the same index ${i}$.
The input process $\recv{i}P$ substitutes in $P$ references to the most immediate variable placeholder with references to the variable sent by the output process $\send{i}{j}{Q}$.
The continuation $\subst{P}{j}{0}$ is then \emph{lowered} --- all variable references are decreased by one.
Reduction is closed under parallel composition (rule $\constr{par}$), restriction (rule $\constr{res}$) and structural congruence (rule $\constr{struct}$) 
--- notably, not under input or output, otherwise the sequencing of actions would not be preserved \cite{Sangio01}.
%In  \autoref{subject-reduction} we prove that if $P$ reduces to $Q$ and $P$ is well-typed, so is $Q$.

\todo{this paragraph below is not clear}
Notice that reduction is effectful: it consumes the channel over which communication occurs.
If the channel is $\constr{external}$ to $P$ (it resides in its typing context) then the context in which $Q$ is typed must change.
To keep track of this information, we lift the index of the channel to the type level.
We use a $dec$ function to decrement the index of the channel every time we come out of a binder.
This function saturates at $\constr{internal}$ --- meaning communication happens internally to the process.
